Word Learning as Network Growth: a Cross-linguistic Analysis

### 2018-01-25 Main.Rmd
cogsci up-date and packrat
changes in CogSci manuscript

@@

Prepare data for age of acqusition analysis (regressions)

@@

>>>>

Here do the power-law analysis and the log-log plots

```{r}
#make a loop
degreeDist <- data.frame(matrix(ncol = 4, nrow = 0))
x <- c("x", "y", "dimension", "language")
colnames(degreeDist) <- x

for (i in language_dict$language_name) {
  #Select data for the language
  data_lang <- data_first_month %>%
    filter(language == i) %>%
    select(language, PAC_assoc, PAC_phono_t2) %>%
    rename(Sem = PAC_assoc, Phono = PAC_phono_t2) %>%
    filter (!is.na(Sem),!is.na(Phono))

  #Do the transfomation
  semList <- data_lang$Sem[data_lang$Sem != 0]
  sem_pl = displ$new(semList)
  sem_est = estimate_xmin(sem_pl)
  sem_pl$setXmin(sem_est)
  sem_dist = plot(sem_pl) %>%
    mutate(dimension='Sem', language  =  i)

  phonoList <- data_lang$Phono[data_lang$Phono != 0]
  phono_pl = displ$new(phonoList)
  phono_est = estimate_xmin(phono_pl)
  phono_pl$setXmin(phono_est)
  phono_dist = plot(phono_pl) %>%
    mutate(dimension='Phono', language = i)

  dist_lang <- bind_rows(sem_dist, phono_dist)

  degreeDist <- bind_rows(degreeDist, dist_lang)

feather::write_feather(degreeDist, "saved_data/degreeDist.feather")
degreeDist <- feather::read_feather("saved_data/degreeDist.feather")

#plot cumulative distributions
ggplot(data = degreeDist,  aes(x=x, y=y, col=dimension))+
  facet_grid(. ~ language)+#, scales = "free") +
  geom_point(#aes(colour = lexical_class),
    #colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  scale_y_log10() + scale_x_log10() +
  theme(aspect.ratio = 1)
  #scale_x_continuous(limits=c(-2,5))+
  #geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  #scale_colour_solarized(name = "")

@@

Prepare data for age of acquisition analysis (regressions)

@@

individ <- individual_both %>%

### 2018-01-25 cogsci/cogsci.Rmd
changes in CogSci manuscript

abstract: 
    "Children tend to learn first the words that are highly connected in the lexical network (i.e., words that are connected to a variety of other words). The process by which connectivity in both the phonological and semantic netwoks come to influence word learning is still not very well understood. One view suggests that learning is driven primarily by *internal* connectivity in the child's available lexicon. Another view suggests that *external* connectivity in the learning environment is what makes words salient and readily learned. The present study tests both scenarios systematically in both the phonological and the the semantic domains, and across 8 languages. We generate the results obtained by Hills et al. (2009) with English semantic networks, and show that external connectivity in the learning environment, rather than internal connectivity, drives growth of both semantic and phonological networks. Finally, we demonstrate that these effects hold cross-linguistically."

keywords:
    "semantic network, phonological network, word learning"

@@

```{r global_options, include=FALSE}
rm(list=ls())

@@

What factors shape vocabulary learning over the course of early childhood? To investigate this question, scientists have adopted multiple research strategies, from controlled laboratory experiments to corpus analysis. One strategy consists in documenting the timeline of words' acquisition, and studying the properies that make words easy or hard to learn. For example, within a lexical category, words that are more frequent in child-directed speech are acquired earlier [@goodman2008]. Other factors include word length, the mean length of utterances in which the word occurs, and how concrete the word is [see @braginsky2016].

@@

Studies that investigted lexical network growth focused on semantic networks using English data only [@steyvers2005; @hills2009; @hills2010].  The novelty of the current study is that it investigates whether phonological networks, like semantic networks, grow by PAC, or if they rather grow by PAT. It also provides a systematic comparision of network growth scenarios in both the phonological and the semantic domains and assesses their relative contribution to the learning process. Moreover, it tests the generality of the findings across eight languages.

The paper is organized as follows. First, we describe the dataset we used, the procedure we followed to construct both semantic and phonological networks. Next, we show the results of the various analyses we conducted comparing network growth scenarios across languages. Then we test the overall contribution of the networks in the learning process relative to other known predictors of age of acquisition (frequency and length). Finally we discuss the major results in relation to known experimental facts in language development.

@@

plot_data_all <- ggplot(data_long, aes(x=value, y=AoA))+
  facet_grid(predictor ~ language)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=correlations, aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("AoA")

@@

# Networks

## Data

We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist. We used the *Words and Sentence* version of the CDI which contains the productive vocabulary of toddlers (age varied between 16 to 36 months). Following previous studies [e.g., @storkel2009; @hills2009], we restricted our analysis to the category of nouns, since there are known discrepancies between the learning of nouns, predicates, and function words [e.g., @braginsky2016]. The age of acquisition was defined by the month at which a word was produced by at least 50% of children [@goodman2008].

@@

With this data, we constructed both semantic and phonological networks.

@@

We used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998]. This dataset was collected by giving adult participants a word (the cue), and asking them to write the first word that comes to mind (the target). For example, when given the word "ball", they might answer with the word "game". A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms. Each node was characterized by its "indegree", which represents the number of links for which the word was the target. Following @hills2009, we used as a proxy for the learning environment, the network constructed using the full set of nouns in the CDI data in each language (e.g., in English this corresponds to the network by 30 months).

@@

We used as a measure of phonological relatedness between two nodes the Levenshtein (edit) distance between their phonological forms. The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.  We generated approximate International Phonetic Alphabet (IPA) trnascriptions from the orthographic transcription, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).**

In previous studies, two nodes were linked if they had an edit distance of 1 [@stokes2010; @storkel2009]. However, in these previous studies the network was built using an adult vocabulary. Here, similar to the approximation we made for the semantic network, we used the full set of nouns in the CDI data as a proxy for phonological connectivity in the learning environment. However, since the children's vocabulary contains very few word pairs with an edit distance of 1, the resulting network was too sparse and uninformative. Thus, we increased the threshold from 1 to 2, that is, two node were related if their edit distance was equal to 1 or 2. Each node was characterized with its degree, i.e., the number of links it shares with other words.

@@

We start by examining how connectivity in the global netowrk influences the age of acqusition. Regardless of the growth mechanism that might have given rise to this netowrk (i.e., PAC or PAT), we expect nodes with the higher degrees in this network to be learned earlier than nodes with the lower degrees. The network was constructed using nouns at the oldest age for which we have CDI data. Figure \ref{fig:data_all} shows how the age of acquisition for each word varies as a function of its degree (or indegree for the semantic network). For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled across languages. The plots show, overall, a negative correlation between the month of acquisition and the degree, indicating that nouns with higher degrees are generally learned earlier.

<!--
```{r }

@@

To test the network growth scenarios, we fit different growth models to the data. We proceeded as follows. We calculated the probability that a word $w_i$, with a growth value $d_i$ would enter the lexicon at a given month, using a softmax function: 
\begin{equation}
 p(w_i)= \frac{e^{\beta d_i}}{\sum_j e^{\beta d_j} }
\end{equation}
Where $\beta$ is the fitting parameter. A positive value of $\beta$ means that words with higher growth values $d_i$ are acquired first, and a negative value means that words with lower growth values are acquired first. As explained in Figure \ref{fig:growth}, each candidate word $w_i$ is characterized with a growth values $d_i$ that depends on the growth scenario tested.  The normalization includes all words that could be learned at that month.

We estimated the parameter $\beta$ using a Bayesian approach. The inference was performed using the probabilisitic programming language  WebPPL [@dippl]. We started with a uniform distribution, and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been actually learned at that month (using formula 1). We ended up with a posterior distribution of $\beta$, which we summarized in Figure \ref{fig:pred_ind}.

@@

The results from both evaluations were very similar and lead essentially to the same conclusions\footnote{we do not show here the resuts of the second evaluation because they were redundant with the results of the first evaluation}. For the semantic network, the results replicate Hills et al.'s finding in English, which was that the semantic network grows by PAC, not by PAT. Moreover, it generalizes this finding to all other languages (with the exception of Russian). For the phonological network, the results show that, generally speaking, PAC again fits the developmental trajectory better than PAT. We note however that PAT, though weaker, fares  better for the phonological networks (where it predicts part of the growth process in some languages such as Croatian, English, Norwegian and Russian) than it does for the semantic networks (where it is rather universally unpredictive).

@@

We saw that the way semantic and phonological information is structured in the learning environment (i.e., PAC) contribute to noun learning across languages. However, we know that other factors influence learning as well [e.g., @braginsky2016]. In what follows, we will investigate how semantic and phonological connectivity interact with two other factors. The first one is word frequency, a well studied factor shown to predict the age of acquisition in a reliable fashion [e.g. @goodman2008]. The second factor is word length, which correlates with phonological connectivity [@pisoni1985].

@@

The present study provided a comprehensive analysis of how lexical connectivity influences the age of acquisition of nouns in toddlers. We compared two network growth scenarios and assessed the relative contribution of phonological and semantic information in 8 languages. Part of the findings largely replicate the results obtained in @hills2009, i.e., semantic networks (based on free associations) grow by preferential acquisition, not by preferential attachment. Another finding was that phonological networks also grow primarily by preferential acquisition, especially when both scenarios (PAT and PAC) were pitted against each other in the same model. These findings generalize well across languages. Moreoever, both semantic and phonological connectivity in the learning environment (i.e., PAC) predict growth in a consistent way across many languages. However, when pitted against other known predictors of age of acquisition (word frequency and length), the effect of word connectivity shows a cross-linguistic variation, predicting learning in some languages, but not in others. Despite this cross-lingusitic variation, both phonological and semantic connectivity contribute to the overall learning (when data is pooled across languages).

@@

A major results of the study is that children start by learning words that have high phonological and semantic similarity with a variety of other words in the learning environment, not in the child's available lexicon.  This suggests that children are sensitive to connectivity even without having first acquired the connected words. How can children indirectly detect highly connected words, and why would such words be more readily learned? In the semantic case, free association can be predicted through the patterns of word co-occurrence [@griffiths07], meaning that highly connected words tend to be the words that co-occur with many other words in various contexts. One possibility, suggested by @hills2010, is that the referents of such words are more easily disambiguated from other potential referents. Such effect was demonstrated by cross-situational learning experiments [@smith2008].
In the phonological case, connectivity is inherently correlated with phonotactic probability [@vitevitch1999]. That is, highly connected words tend to be made of frequent sound sequences. We know even infant (whose vocabulary is still very rudimentary) develop a sensitivity for high frequency sound sequences in the ambient language [@jusczyk1994]. Interestingly, it was shown that phonotactic probability facilitates learning and recognition of novel words in toddlers and preschoolers [@storkel2001;  @higgins2014]. Thus, children's ability to keep track of co-occurrence statistics (both at the semantic and phonological level) might explain their sensitivity and preference for highly connected words in the learning envirnoment.

Finally, this study shares a number of limitations with previous studies using similar datasets. For instance, we used normative age of acquisition. However, individual children may follow different learning trajectories. The use of longitudinal data would allow us to assess how the aggregate behavior relates to these individual trajectories [e.g., typical vs. late talkers, @beckage2011]. Moreover, the results obtained in this study provide correlational but not causal evidence. Thus, conclusions drawn from our network analysis would require parallel evidence, especially from controlled behavioral experiments.

>>>>

abstract:

    "Children tend to produce first the words that are connected to a variety of other words along both the phonological and the semantic dimensions. Though this connectivity effect has been extensively documented, little is known about the underlying developmental mechanism.  One view suggests that learning is primarily driven by a network growth model where highly connected words in the child's ealy lexicon attract similar words. Another view suggests that learning is driven, not by highly connected words in the early internal lexicon, but by highly connected word in the external learning environment. The present study tests both scenarios systematically in both the phonological and the semantic domains, and across 8 languages. We show that external connectivity in the learning environment drives growth in both the semantic and the phonological networks, and that this pattern is consistent cross-linguistically. The findings suggest a word learning mechanism where children harness their statistical learning abilities to (indirectly) detect and learn highly connected words in the learning environment."

keywords:
    "semantic network, phonological network, network growth, mechanism of word learning"

@@

<!-- Children tend to learn some words typically at an earlier age than others. Researchers have documented many word properties that influence the order of acquisition of words.  This paper investigates strcutural properties that characterize how words are related to each other in the lexicon.  -->
```{r global_options, include=FALSE}
rm(list=ls())

@@

What factors shape vocabulary learning over the course of early childhood? To investigate this question, scientists have adopted multiple research strategies, from controlled laboratory experiments to corpus analysis. One strategy consists in documenting the timeline of words' acquisition, and studying the properties that make words easy or hard to learn. For example, within a lexical category, words that are more frequent in child-directed speech are acquired earlier [@goodman2008]. Other factors include word length, the mean length of utterances in which the word occurs, and how concrete the word is [see @braginsky2016].

@@

Studies that investigated lexical network growth focused on semantic networks using English data only [@steyvers2005; @hills2009; @hills2010].  The novelty of the current study is that it investigates whether phonological networks, like semantic networks, grow by PAC, or if they rather grow by PAT. It also provides a systematic comparison of network growth scenarios in  the phonological and the semantic domains and assesses their relative contribution to the learning process. Moreover, it tests the generality of the findings across eight languages.

The paper is organized as follows. First, we describe the dataset we used, the procedure we followed to construct both semantic and phonological networks. Next, we show the results of the various analyses we conducted comparing network growth scenarios across languages. Then we test the overall contribution of the networks in the learning process relative to other known predictors of age of acquisition (frequency and length). Finally we discuss the major results in relation to known experimental facts in language development, and we speculate about the potential learning mechanism that might drive early vocabulary learning.

@@

plot_data_all <- ggplot(data_long, aes(x=value, y=AoA))+
  facet_grid(predictor ~ language)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_bw()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=correlations, aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("AoA")

@@

#Import data from saved
degreeDist <- feather::read_feather("../saved_data/degreeDist.feather")

plot_dist <- ggplot(data = degreeDist,  aes(x=x, y=y, col=dimension))+
  facet_grid(. ~ language)+
  geom_point(size = 0.5, alpha = 0.5) +
  scale_y_log10() + scale_x_log10() +
  theme_bw()+
  theme(aspect.ratio = 1)+
  xlab("degree") +ylab("probability")

ggsave("figs/degreeDist.png", plot = plot_dist, width = 7, height = 3)

```{r degree_distribution, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:degree_distribution}Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages. A perfect power law distribution should appear as a straight line in this graph."}
plot_dist
#img <- png::readPNG("figs/data_all.png")
#grid::grid.raster(img)

# Networks
## Data
We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist. We used the *Words and Sentence* version of the CDI which contains the productive vocabulary of toddlers (age varied between 16 to 36 months). Following previous studies [e.g., @storkel2009; @hills2009], we restricted our analysis to the category of nouns. The age of acquisition was defined by the month at which a word was produced by at least 50% of children [@goodman2008].

@@

@@

We used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998]. This dataset was collected by giving adult participants a word (the cue), and asking them to write the first word that comes to mind (the target). For example, when given the word "ball", they might answer with the word "game". A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms. Each node was characterized by its "indegree", which represents the number of links for which the word was the target. To model growth from month to month, we constructed a different network at each month, made of words that have been learned at that month. Following @hills2009, we used as a proxy for the learning environment, the network constructed using the full set of nouns in the CDI data in each language (e.g., in English this corresponds to the network by 30 months).

@@

We used as a measure of phonological relatedness between two nodes the Levenshtein (edit) distance between their phonological forms. The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.  We generated approximate International Phonetic Alphabet (IPA) transcriptions from the orthographic transcription, across languages, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).**

In previous studies, two nodes were linked if they had an edit distance of 1 [@stokes2010; @storkel2009]. However, in these previous studies the network was built using an adult vocabulary. Here, similar to the approximation we made for the semantic network, we used the full set of nouns in the CDI data as a proxy for phonological connectivity in the learning environment. However, since the children's vocabulary contains very few word pairs with an edit distance of 1, the resulting network was too sparse and uninformative. Thus, we increased the threshold from 1 to 2, that is, two node were related if their edit distance was equal to 1 or 2. Each node was characterized with its degree, i.e., the number of links it shares with other words. <!-- Moreover, and in order to model growth from month to month, we constructed a different network at each month, made of words that have been learned at that month. -->

@@

## Preliminary analysis
We start by examining how connectivity in the global network influences the age of acquisition. Regardless of the growth mechanism that might have given rise to this network (i.e., PAC or PAT), we expect nodes with the higher degrees in this network to be learned earlier than nodes with the lower degrees. The global network was constructed using nouns at the oldest age for which we have CDI data. Figure \ref{fig:data_all} shows how the age of acquisition for each word varies as a function of its degree (or indegree for the semantic network). For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled across languages. The plots show, overall, a negative correlation between the month of acquisition and the degree, indicating that nouns with higher degrees are generally learned earlier.

We also analysed the global network degree distribution. PAT is known to generate networks with a power-law degree distribution [@barabasi99]. Thus, if the networks display this property, it means that PAT cannot be ruled out *a priori* as a potential growth mechanism. In contrast, if there is strong evidence against a power law distribution, then PAT (but not PAC) can be ruled out.  The distributions are shown in Figure \ref{fig:degree_distribution}. Overall, the results do not provide strong evidence against a power-law distribution. Moreover, the degree to which the distribution approximates a power law varies across dimension and languages. For a more conclusive test, we fit explicit growth models to the data (next section).
<!--
```{r }

@@

To test the network growth scenarios, we fit different growth models to the data. We proceeded as follows. We calculated the probability that a word $w_i$, with a growth value $d_i$ would enter the lexicon at a given month, using a softmax function: 
\begin{equation}
 p(w_i)= \frac{e^{\beta d_i}}{\sum_j e^{\beta d_j} }
\end{equation}
Where $\beta$ is the fitting parameter. A positive value of $\beta$ means that words with higher growth values $d_i$ are acquired first, and a negative value means that words with lower growth values are acquired first. As explained in Figure \ref{fig:growth}, each candidate word $w_i$ is characterized with a growth values $d_i$ that depends on the growth scenario tested.  In PAT, the growth value of a given word is equal to the average degree of the existing nodes that it would attach to. In PAC, the growth value of a word is equal to its degree in the entire network.  The normalization includes all words that could be learned at that month.

We estimated the parameter $\beta$ using a Bayesian approach. The inference was performed using the probabilistic programming language  WebPPL [@dippl]. We started with a uniform distribution, and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been actually learned at that month (using formula 1). We ended up with a posterior distribution of $\beta$, which we summarized in Figure \ref{fig:pred_ind}.

@@

The results from both evaluations were very similar and lead essentially to the same conclusions\footnote{we do not show here the results of the second evaluation because they were redundant with the results of the first evaluation}. For the semantic network, the results replicate Hills et al.'s finding in English, which was that the semantic network grows by PAC, not by PAT. Moreover, it generalizes this finding to all other languages (with the exception of Russian). For the phonological network, the results show that, generally speaking, PAC again fits the developmental trajectory better than PAT. We note however that PAT, though weaker, fares  better for the phonological networks (where it predicts part of the growth process in some languages such as Croatian, English, Norwegian and Russian) than it does for the semantic networks (where it is rather universally unpredictive).

@@

We saw that the way semantic and phonological information is structured in the learning environment (i.e., PAC) contribute to noun learning across languages. However, we know that other factors influence learning as well [e.g., @braginsky2016]. In what follows, we will investigate how semantic and phonological connectivity interact with two other factors. The first one is word frequency, a well studied factor shown to predict the age of acquisition in a reliable fashion [e.g. @goodman2008]. The second factor is word length, which correlates with phonological connectivity. <!-- [@pisoni1985].-->

@@

The present study provided a comprehensive analysis of how lexical connectivity influences the age of acquisition of nouns in toddlers. We compared two network growth scenarios and assessed the relative contribution of phonological and semantic information in 8 languages. Part of the findings largely replicate the results obtained in @hills2009, i.e., semantic networks (based on free associations) grow by preferential acquisition, not by preferential attachment. Another finding was that phonological networks also grow primarily by preferential acquisition, especially when both scenarios (PAT and PAC) were pitted against each other in the same model. These findings generalize well across languages. Moreover, both semantic and phonological connectivity in the learning environment (i.e., PAC) predict growth in a consistent way across many languages. However, when pitted against other known predictors of age of acquisition (word frequency and length), the effect of word connectivity shows a cross-linguistic variation, predicting learning in some languages, but not in others. Despite this cross-linguistic variation, both phonological and semantic connectivity contribute to the overall learning (when data is pooled across languages).

@@

A major results of the study is that children start by learning words that have high phonological and semantic similarity with a variety of other words in the learning environment, not in the child's available lexicon.  This suggests that children are sensitive to connectivity even without having first acquired the connected words. How can children indirectly detect highly connected words, and why would such words be more readily learned? In the semantic case, free association can be predicted through the patterns of word co-occurrence [@griffiths07], meaning that highly connected words tend to be the words that co-occur with many other words in various contexts. One possibility, suggested by @hills2010, is that the referents of such words are more easily disambiguated from other potential referents. Such effect was demonstrated by cross-situational learning experiments [@smith2008].

In the phonological case, connectivity is inherently correlated with phonotactic probability [@vitevitch1999]. That is, highly connected words tend to be made of frequent sound sequences. We know even infant (whose vocabulary is still very rudimentary) develop a sensitivity for high frequency sound sequences in the ambient language [@jusczyk1994]. Interestingly, it was shown that phonotactic probability facilitates learning and recognition of novel words in toddlers and preschoolers [@storkel2001;  @higgins2014]. Thus, children's ability to keep track of co-occurrence statistics (both at the semantic and phonological level) might explain their sensitivity and preference for highly connected words in the learning environment.

Finally, this study shares a number of limitations with previous studies using similar datasets. <!--For instance, we used normative age of acquisition. However, individual children may follow different learning trajectories. The use of longitudinal data would allow us to assess how the aggregate behavior relates to these individual trajectories [e.g., typical vs. late talkers, @beckage2011]. Moreover,--> In particular, the results provide correlational but not causal evidence. Thus, the conclusions of this study  require parallel evidence, especially from controlled behavioral experiments.
